\begin{thebibliography}{9}

\bibitem{Sateia}	
M. J. Sateia, “International Classification of Sleep Disorders-Third Edition,” Chest, vol. 146, no. 5, pp. 1387–1394, Nov. 2014. 
	

\bibitem{Horaud}
Horaud, R.; Hansard, M.; Evangelidis, G.; Ménier, C. An overview of depth cameras and range scanners based on time-of-flight technologies. Mach. Vis. Appl. {\bf 2016}, {\em 27}, 1005–1020.

%Reference 2
\bibitem{Lefloch} 
Lefloch, D.; Nair, R.; Lenzen, F.; Schäfer, H.; Streeter, L.; Cree, M.J.; Koch, R.; Kolb, A. LNCS 8200 - Technical Foundation and Calibration Methods for Time-of-Flight Cameras;

% Reference 3
\bibitem{Zhang}
Zhang, H.; Wei, Q.; Jiang, Z. 3D reconstruction of space objects from multi-views by a visible sensor. Sensors (Switzerland) 2017, 17, 8–13.

% Reference 4
\bibitem{Bhandari}
Bhandari, A.; Kadambi, A.; Whyte, R.; Barsi, C.; Feigin, M.; Dorrington, A.; Raskar, R. Resolving multi-path interference in time-of-flight imaging via modulation frequency diversity and sparse regularization. {\em Optics letters} {\bf 2014}, {\em 39}, 1705-1708.

% Reference 5
\bibitem{Jimenez}
Jiménez, D.; Pizarro, M.; Mazo, M.; Palazuelos, S. Modeling and correction of multipath interference in time of flight cameras. {\em Image and Vision Computing} {\bf 2014}, {\em 32}, 1-13.

% Reference 6
\bibitem{JGodbaz}
Godbaz, J. P.; Cree, M. J.; Dorrington, A. A. Closedform inverses for the mixed pixel/multipath interference problem in amcw lidar. {\em IS\&T/SPIE Electronic Imaging} {\bf 2012}, {\em 8296}, 829618-829618.

% Reference 7
\bibitem{Kirmani}
Kirmani, A.; Benedetti, A.; Chou, P. A. Spumic: Simultaneous phase unwrapping and multipath interference cancellation in time-of-flight cameras using spectral methods. {\em ICME} {\bf 2012}, 1-6.

% Reference 8
\bibitem{Volak2018}
Volak, J.; Koniar, D.; Jabloncik, F.; Hargas, L. A Study on OSAS Diagnostics Supported by RGB-D Imaging. {\em 2018 41st International Conference on Telecommunications and Signal Processing (TSP)} {\bf 2018}, 1-4.

% Reference 9
\bibitem{Kim}
Kim, Y.M.; Chan, D.; Theobalt, C.; Thrun, S. Design and calibration of a multi-view TOF sensor fusion system. 2008 IEEE Comput. Soc. Conf. Comput. Vis. Pattern Recognit. Work. CVPR Work. 2008.

% Reference 10
\bibitem{Buttgen}
Buttgen, B.; El Mechat, M. H. A.; Lustenberger, F.; Seitz, P. Pseudonoise optical modulation for real-time 3-d imaging with minimum interference. {\em Circuits and Systems I: Regular Papers} {\bf 2007}, {\em 54}, 2109-2119.

% Reference 11
\bibitem{Whyte}
Whyte, R. Z.; Payne, A. D.; Dorrington, A. A., Cree M. J. Multiple range imaging camera operation with minimal performance impact. {\em SPIE} {\bf 2010}, {\em 8296}, 75380I-75380I.

% Reference 12
\bibitem{Seitz}
Buttgen, B.; Seitz, P. Robust optical time-of-flight range imaging based on smart pixel structures. {\em Circuits and Systems I: Regular Papers} {\bf 2008}, {\em 55}, 1512-1525.

% Reference 13
\bibitem{Lianhua}
Lianhua, L.; Xiang, S.; Yang, Y.; Li, Y. Multi-camera interference cancellation of time-of-flight (TOF) cameras. {\em ICIP} {\bf 2015}.

% Reference 14
\bibitem{Lee}
Lee, J.; Gupta, M. Stochastic Exposure Coding for Handling Multi-ToF-Camera Interference. 2020, 7879–7887.

% Reference 15
\bibitem{Bulczak}
Bulczak, D.; Lambers, M., Kolb, A. Quantified, Interactive Simulation of AMCW ToF Camera Including Multipath Effects. {\em Sensors} {\bf 2017}.

% Reference 16
\bibitem{Lange}
Lange, B. 3D Time-of-flight distance measurement with custom solid-state image sensors in CMOS/CCD-technology. {\em Ph.D. dissertation, Department of Electrical Engineering and Computer Science at University of Siegen} {\bf2000}.

% Reference 17
\bibitem{Han}
Han, X.F.; Jin, J.S.; Wang, M.J.; Jiang, W.; Gao, L.; Xiao, L. A review of algorithms for filtering the 3D point cloud. Signal Process. Image Commun. 2017, 57, 103–112.

% Reference 18
\bibitem{Pirotti}
Pirotti, F.; Ravanelli, R.; Fissore, F.; Masiero, A. Implementation and assessment of two density-based outlier detection methods over large spatial point clouds. Open Geospatial Data, Softw. Stand. 2018, 3.

% Reference 19
\bibitem{Corso}
Corso, J.; Garcia-Almirall, P.; López, D.; Casals, J. Disclosure of Temporary Exposures as Permanent Website Applications through the Patrimonial Survey. IOP Conf. Ser. Mater. Sci. Eng. 2017, 245.

% Reference 20
\bibitem{Balta}
Balta, H.; Velagic, J.; Bosschaerts, W.; De Cubber, G.; Siciliano, B. Fast Statistical Outlier Removal Based Method for Large 3D Point Clouds of Outdoor Environments. IFAC-PapersOnLine 2018, 51, 348–353.

% Reference 21
\bibitem{Arroyo}
Arroyo, F.T.; Eguilaz, M.M. Industrial Technology Engineering Reconstruction of scenes using a hand-held range imaging camera. 2017.

% Reference 22
\bibitem{Guerrero}
Guerrero, P.; Kleiman, Y.; Ovsjanikov, M.; Mitra, N.J. Learning Local Shape Properties from Raw Point Clouds. 2018, 37.

% Reference 23
\bibitem{Rakotosaona}
Rakotosaona, M.J.; La Barbera, V.; Guerrero, P.; Mitra, N.J.; Ovsjanikov, M. PointCleanNet: Learning to Denoise and Remove Outliers from Dense Point Clouds. Comput. Graph. Forum 2020, 39, 185–203.

% Reference 24
\bibitem{Yahya}
Yahya, A.A.; Tan, J.; Su, B.; Liu, K. Video Denoising Based on Spatial-Temporal Filtering. In {\em Proceedings of the 2016 6th International Conference on Digital Home (ICDH)}; IEEE: Guangzhou, China, 2016; pp. 34–37.

% Reference 25
\bibitem{Volak2019}
Volak, J.; Koniar, D.; Jabloncik, F.; Hargas, L.; Janisova, S. Interference artifacts suppression in systems with multiple depth cameras. In {\em Proceedings of the 2019 42nd International Conference on Telecommunications and Signal Processing (TSP)}; IEEE: Budapest, Hungary, 2019; pp. 472–476

% Reference 26
\bibitem{Lu}
Lu, D.; Lu, X.; Sun, Y.; Wang, J. Deep feature-preserving normal estimation for point cloud filtering. Comput. Des. 2020, 125, 102860.

% Reference 27
\bibitem{Schaller}
Schaller, C.; Adelt, A.; Penne, J.; Hornegger, J. Time-of-Flight sensor for patient positioning. Med. Imaging 2009 Vis. Image-Guided Proced. Model. 2009, 7261, 726110.

% Reference 28
\bibitem{Jia}
Jia, C.; Yang, T.; Wang, C.; Fan, B.; He, F. A new fast filtering algorithm for a 3D point cloud based on RGB-D information. PLoS One 2019, 14, e0220253.

\end{thebibliography}